The title

### 2020-01-16 test2.tex
citation added

@@

We used R (Version 3.6.1; R Core Team, 2019) for all our analyses.

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

>>>>

\texttt{\{r\ setup,\ include\ =\ FALSE\}\ library("papaja")}

\texttt{\{r\ analysis-preferences\}\ \#\ Seed\ for\ random\ number\ generation\ set.seed(42)\ knitr::opts\_chunk\$set(cache.extra\ =\ knitr::rand\_seed)}

@@

We used \texttt{r\ cite\_r("r-references.bib")} for all our analyses.

@@

\texttt{\{r\ create\_r-references\}\ r\_refs(file\ =\ "r-references.bib")}

@@

\hypertarget{refs}{}
